---
title: "aapa - data panel"
author: "Max Probable"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aapa - data panel}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Package aapa operates on the output from companion package aabd, applying more-or-less standard operations in a more-or-less standard sequence, with options to customise at each step. The underlying pattern uses function names in a numerical sequence, such that if all operations starting with a given number are complete, then operations on the next number can proceed.  This defines processing 'chunks' which can be done in parallel, and 'stages' which need to be done serially.

## Companion packages

* aautil : contains **utility** functions used in these examples and internally in the package.
* aabd : **download** is the package which generates the input panels, stored in RData
* aate : **category** builds and manages industry trees and fractional industry classification

## Input and output data

* inputs are in root.global/BDH/derive-000, with one RData file per panel
* inputs go to root.global/BDH/derive-001, similarly structured

## Session

In the following, it matters that aatopselect() is set before aapa is loaded, because the .onLoad sets global variables.  [This is not totally satisfactory.]

```{r, eval = FALSE}
require(aautil)
aatopselect("test")
require(aapa)
require(testthat)
deraapa()
```

After processing, access to the data is comparatively fast and scaleable
```{r}
library(aapa)
aatopselect("test")
cor(getstep("x0703redv"),us='c')
```

## Customisation
Adding additional functions to the package, with appropriate names, causes them to automatically be executed within deraapa() at a 'step' which corresponds to the numeric part of the name. So for example a function beginning 'x07' will be run at the end, and can take dependencies on all preceding steps.
